---
title: "Tech Stack"
::: {.panel-tabset .nav-pills}
---

I've worked with many tools over the course of my several-year career, but two have made a particular mark on my professional experience and education: Alteryx and the R language.

::: {#Alteryx .panel-tabset .nav-pills}
## R

R is programming languages designed for statistics and graphics.

However, it has evolved considerably in recent years, mainly due to the Tidyverse ecosystem which also makes it a powerful tool in the area of Business Intelligence or Data Engineering.

Example of its great BI capabilities is how You can create tables.

```{r echo=FALSE ,warning=FALSE,error=FALSE,message = FALSE}
library(tidyverse)
library(gtExtras)
library(plotly)
library(gt)
library(scales)
library(patchwork)
library(ggtext)

Bands <- readRDS('data/Bands.RDS')
BandsStats <- readRDS('data/BandsStats.RDS')

BandsHeaders <- c("Band","Events","Total Contracts","Average contract",'Highest value')
names(BandsStats) <- BandsHeaders

BandsStats <- 
  BandsStats |>
  select(-c(Events)) |>
  arrange(desc(`Average contract`))
```

```{r,error=FALSE,message = FALSE,warning=FALSE,echo=TRUE}
BandsStats |>
  gt() |>
  tab_header(
  title = "Most expensive bands") |> 
  fmt_currency(columns = c("Total Contracts","Average contract",'Highest value')) |>
  gt_color_rows(2:4, palette = "ggsci::blue_material") |>
  tab_options(
    heading.subtitle.font.size = 12,
    heading.align = "left",
    table.border.top.color = "white",
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    table.align = "left"
  ) |>
  tab_source_note(md(" **Data**: Music agency"))

```

## Alteryx

Alteryx is low code platform designed to perform ETL process
:::
